\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[hidelinks]{hyperref}
    \usepackage{fontawesome}
    \usepackage{hyphenat}
    \usepackage{fancyhdr}
    \usepackage[english]{babel}
    \usepackage[usenames,dvipsnames]{color}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% % Adjust margins
\addtolength{\oddsidemargin}{-0.3in}
\addtolength{\evensidemargin}{-0.3in}
\addtolength{\textwidth}{0.6in}
% \addtolength{\topmargin}{-0.1in}
% \addtolength{\footskip}{-0.5in}

% \addtolength{\textheight}{1.0in}

% \urlstyle{same}

% \raggedbottom
% \raggedright
% \setlength{\tabcolsep}{0in}

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	\textbf{\Huge \scshape {Amit Timalsina}} \\ \vspace{3pt}
    \small
    \href{https://github.com/amit-timalsina}{github.com/amit-timalsina}
    $|$
    \href{https://www.linkedin.com/in/amittimalsina}{linkedin.com/in/amittimalsina}
    $|$
    \href{https://selftaughtamit.medium.com/}{selftaughtamit.medium.com}
    $|$
    \href{mailto:amittimlasina21@gmail.com}{amittimalsina21@gmail.com} \\
\end{center}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Consultant} \hfill Remote\\
\textit{Senior Software Consultant (GenAI, ML, Backend)} \hfill September 2024 - Ongoing\\
{Consulting on LLM integration for extraction, RAG, Agentic use-cases.}
\vspace{-1mm}
\begin{itemize} \itemsep 0pt
	\item Built PDF parser for clinical protocols that returned layout conserved structured output. This improved F1 of chunk retrieval by 60\% absolute and accuracy of entity extraction by 50\% absolute.
	\item Processed 200k clinical protocols enabling new analytics services (e.g., "How often is age inclusion criteria used in trials?"). Handled rate limits, edge cases, and tight deadlines across multiple LLM providers (Anthropic, Llama).
	\item Built RAG chat application over clinical protocol extracted data in Snowflake, achieving 95\% recall@10. Internal stakeholders reported high satisfaction, product ready for customer deployment.
    \item Built OMR extraction using VLM, YOLO, and LLM in 1 week for a startup, deployed to production in 2 weeks. 
	\item Implemented Langfuse for LLM observability, reducing debugging time by 80\% and enabling customer-level spend tracking. Led cross-functional collaboration with SRE team for in-house deployment.
\end{itemize}

\textbf{Kniru} \hfill Bangalore, India\\
\textit{Founding Engineer, SDE-2} \hfill January 2024 - September 2024\\
{First full-time hire at pre-seed fintech startup. End-to-End (AI, Backend, Frontend) productionalization of core features.}
\vspace{-1mm}
\begin{itemize} \itemsep 0pt
	\item Built multi-agentic RAG chat system serving 80 MAU with 10 daily queries, achieving 70\%+ user satisfaction and 50\% retention. System handled spending analysis, tax advising, investment, and retirement planning through specialized agents accessing PostgreSQL, vector database, and Web Search APIs.
	\item Architected notification engine serving 300 users with 95\% delivery success rate and 20\% engagement. Built event-based architecture with 100+ notification templates, delivering 3 notifications per user daily.
	\item Designed chat-based onboarding experience improving completion rate from 70\% to 90\%. Created "WOW moment" by providing personalized financial insights during onboarding.
	\item Implemented OWASP guardrails against LLM vulnerabilities, Langsmith tracing, and cost-efficient evaluation suite. Mentored junior engineers in AI and backend development.
\end{itemize}

\textbf{Docsumo} \hfill Bangalore, India\\
\textit{Team Lead} \hfill April 2023 - January 2024\\
{Lead team of two engineers to build and maintain internal dev tools for developer efficiency.}
\vspace{-1mm}
\begin{itemize} \itemsep 0pt
	\item Developed end-to-end pipleine for reproducibility of models and evaluation metrics by utilizing versioned data store (DVC, GCS, Gitlab). Reduced benchmarking experiment time by 50\% and GPU resources waste which was caused by incorrect experiments and no bechmark datasets. 
	\item Developed centralized evaluation suite ensuring 100\% accurate metric comparison across experiements. Single-point bug fixes improved evaluation reliability and reduced maintenance overhead.
	\item Created data assets dashboard with metadata across prod, staging, and testing environments. It also had weekly model performance tracking of all customer accounts, used by teams to evaluate improvements and degradation.
	\item Led architectural decisions for tracing, evaluation frameworks, and uniform benchmarking datasets across multiple document types.
\end{itemize}

\textit{Machine Learning Engineer} \hfill May 2022 - January 2024\\
\vspace{-1mm}
\begin{itemize} \itemsep 0pt
	\item Built LLM-powered key-value extractor reducing annotation time by 70\% and enabling faster support for new document types. Implemented layout parsing, zero/few-shot prompting, and confidence scoring.
	\item Fine-tuned Visual Document Understanding models for NER tasks achieving 91\%+ accuracy across document types. Deployed 10+ models to production serving enterprise customers with 500k+ ARR.
	\item Led multilingual KV extraction research for Spanish bank statements and Chinese invoices, achieving 7\% accuracy improvement from baseline. Improved customer retention through enhanced international document support.
	\item Built table header classifier with FastText and fuzzy ensemble achieving 96\% accuracy. Created inference API for production deployment.
\end{itemize}

\textbf{Nepal Can Move} \hfill Remote\\
\textit{Junior Machine Learning Engineer} \hfill July 2021 - March 2022\\
\vspace{-1mm}
\begin{itemize} \itemsep 0pt
	\item Built and deployed delivery failure prediction system processing 100k-150k monthly deliveries, reducing failure rate from 25\% to 15\% and saving Re 6 lakhs (5k USD) in first month. Optimized for 87\% recall with limited features, implemented automated CI/CD pipeline for weekly retraining and batch feature generation.
	\item Developed invoice information extraction system reducing processing time from 2 mins to 4 secs per document with 87\% token-level accuracy. Built end-to-end pipeline using OpenCV, pyTesseract, spaCy, and Transformers.
	\item Researched recommendation engine prototype achieving 75\% accuracy on top@10 retrieval using TensorFlow Recommenders, benchmarked on 100k MovieLens ratings for potential e-commerce integration.
	\item Built medical diagnosis sequence generation model using BERT architecture for 25 diseases, achieving 0.83 F1 score as POC for healthcare business venture.
\end{itemize}

\vspace*{2mm}

%==== Products ====%
\header{Products}
\vspace{1mm}

\textbf{Blintic AI} \hfill \href{https://www.blinticai.com/}{blinticai.com} $|$ \href{https://app.blinticai.com}{app.blinticai.com}\\
\textit{No-Code AI Agent Platform for Customer Support} \hfill January 2025 - Ongoing\\

{Built end-to-end no-code platform enabling businesses to create AI agents for customer support without technical expertise.}
\begin{itemize} \itemsep 0pt
    \item Developed full-stack platform with Next.js frontend and FastAPI backend, serving 10+ demo customers with custom agent orchestration and hybrid retrieval (dense embeddings + BM25 + Jina reranker) for comprehensive knowledge base search.
    \item Built custom agent orchestrator supporting multiple data sources (text, files, URLs, website scraping) and custom actions (API calls) for external integrations, enabling seamless workflow automation and third-party system connectivity.
    \item Implemented intelligent support escalation system with team tagging and custom chat embed UI customization, allowing businesses to maintain control over complex queries while providing personalized customer experiences.
    \item Architected scalable infrastructure on Vercel and Google Cloud Run with PostgreSQL database, Supabase auth, and comprehensive observability using Langfuse for production monitoring and performance tracking.
    \item Planned for open-source release to democratize AI agent development for customer support and enable community contributions to the platform.
\end{itemize}
\vspace*{2mm}


%==== Projects ====%
\header{Projects}
{\textbf{Document Classification}}\hfill \href{https://github.com/amit-timalsina/document-classification}{Github}
\vspace{-2mm}
\begin{itemize} \itemsep 0pt
    \item Common OCR interface for closed-source providers like Google Vision and open source providers like Pytesseract.
    \item Training, Evaluation, and Inference support for Fasttext, Small Language Models (BERT, etc), Vision Language Models (like LayoutLM), and LLMs.
\end{itemize}

{\textbf{Cricket Fitness Analysis}}\hfill \href{https://github.com/amit-timalsina/sports-analysis}{Github} \\
FastAPI, Postgres, Supabase, Docker, WebSocket, Langfuse
\vspace{-1mm}
\begin{itemize} \itemsep 0pt
    \item Log fitnes, coaching, match, and rest day using voice input with AI follow up questions. Input is transcribed using OpenAI whisper and then converted into structured ouptut using OpenAI structured output.
    \item Developed progress tracking dashboard with charts for weekly performance visualization, enabling players to monitor training, coaching, matches, and rest days systematically.
\end{itemize}
\vspace*{2mm}

%==== Skills ====%
\header{Skills}
\vspace{-1mm}
\begin{itemize} \itemsep 0pt
    \item \textbf{Language and Technology:} Python, Bash, Sqlite, Postgres, Docker, AWS, GCP
    \item \textbf{Framework \& Library:} FastAPI, Flask, Pydantic, PyTorch, TensorFlow (Keras), Transformers, HuggingFace Hub, FastText, XGBoost, OpenCV, Scikit-learn, Instructor, OpenAI, Langchain, Llama-index, CrewAI, Autogen, Qdrant VDB, Pinecone VDB, Amazon SageMaker, MLFlow, DVC, NumPy, Pandas, NLTK, spaCy
    \item \textbf{Machine Learning:} Prompting, Agentic Systems, RAG, Information Extraction, Document AI, Transfer Learning, PEFT, Fine-tuning, MLOps, Applied Statistics and Probability, Machine Learning and Deep Learning algorithms, NLP and NLU, Recommendation Systems
\end{itemize}
\vspace{2mm}

%==== Awards and Achievements ====%
\header{Awards and Achievements}
\textbf{Young Scientist of Nepal} \hfill Young Scientists Summit (RECAST)\\
Won the first position in Computer Science department of 5 th Young Scientist Summit (YSS). \hfill 2020\\
\vspace*{2mm}
\textbf{Glocal 20under20 of 2020} \hfill Glocal Teen Hero\\
Selected as Glocal 20Under20 for 2020 Batch as a "The Early Change Makers". \hfill 2020\\
\vspace*{2mm}

%==== Education ====%
% \header{Education}
% \textbf{Sainik Awasiya Mahavidyalaya}\hfill Bhaktapur, Nepal\\
% Diploma Computer Engineering \hfill July 2019 - Oct 2021\\
% \vspace{2mm}
% \textbf{Coursera}\hfill Remote\\
% Deep Learning Specialization\hfill Aug 2020 - Nov 2020\\
% \vspace{2mm}
% \textbf{Coursera}\hfill Remote\\
% DeepLearning.ai TensorFlow Developer Specialization\hfill Aug 2020 - Nov 2020\\
% \vspace{2mm}
% \textbf{Coursera}\hfill Remote\\
% Google Project Management: Professional Certificates\hfill Oct 2022 - Nov 2023\\
% \vspace{4mm}

\ 
\end{document}